---
format:
  html:
    toc: true
    standalone: false
    title-block-style: none
    ascii: true
  pdf:
    fig-dpi: 1000
    fig-pos: "H"
  docx:
    fig-dpi: 1000
execute:
  echo: false
  warning: false
  error: false
engine: knitr
---

## Current Delta Hydrologic Conditions

Last updated: *`r format(Sys.Date(), "%B %d, %Y")`*

```{r}
#| label: setup
#| echo: false
#| output: false

library(tidyverse)
library(here)
library(kableExtra)
library(flextable)
library(magick)
library(readr)
library(patchwork)

project <- here()
source(here(project, 'source_code/zoi_maps_query.R'), echo = FALSE)
source(here(project, 'source_code/hydro_data_extraction.R'), echo = FALSE)
mapList <- list.files(here(project, 'zoi_maps/'), full.names = TRUE)
```

### Operational and Regulatory Conditions

Entrainment management is the current controlling factor. See most recent weekly outlook for more information.

### Current Conditions

Most recent inflow at Freeport in the Sacramento River and Vernalis in the San Joaquin River is `r fpt` and `r vns` cfs respectively.  Most recent 1-day, 5-day, and 14-day OMRI measurements were `r omr_text`, `r omr5D_text`, and `r omr14D_text` cfs respectively, and most recent export data were `r cvp` cfs for Jones Pumping Plant and `r swp` cfs for Henry O. Banks Pumping Plant.
```{r}
#| include: false
export_plot <- pumping_clean %>%
  ggplot(aes(x = date)) +
  labs(y = 'Exports (cfs)') +
  geom_col(aes(y = value, fill = facility), color = "black") +
  scale_fill_manual(values = c('#0072B2', 'gray80')) +
  scale_x_date(date_breaks = '2 weeks', date_labels = '%b %d') +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text = element_text(size = 15),
        legend.text = element_text(size =15),
        legend.title = element_text(size = 15),
        legend.position = "bottom",
        axis.title= element_text(size = 15))
export_plot
```

```{r}
#| include: false
# Pull annotation start value for flow plot
ann_start_FPT <- flow_clean %>% filter(station == "FPT", date == date(start)) %>% pull(flow)
ann_start_VNS <- flow_clean %>% filter(station == "VNS", date == date(start)) %>% pull(flow)

flow_plot <- flow_clean %>%
  ggplot(aes(x = date)) +
  annotate("label", x = date(start)+2, y = ann_start_FPT-3000, label = "FPT", color = "#388715")+
  annotate("label", x = date(start)+2, y = ann_start_VNS+3000, label = "VNS", color = "gray20")+
  labs(y = 'Flow (cfs)') +
  geom_line(aes(y = flow, color = station)) +
  scale_color_manual(values = c("#43a419", "gray15")) +
  scale_x_date(date_breaks = '2 weeks', date_labels = '%b %d') +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.text = element_text(size = 15),
        axis.title= element_text(size = 15))
flow_plot
```

```{r}
#| include: false
omr_plot <- 
  ggplot() +
  geom_rect(data= triggers_shading, aes(xmin= date_implemented, xmax= implementation_end), ymin=-Inf, ymax= Inf, 
            fill= "gray70", alpha= 0.5, inherit.aes = FALSE)+
  geom_line(data = omr_clean, aes(x = date, y = value, color = measure), linewidth = 1) +
  geom_vline(data = triggers_clean, aes(xintercept = date), linewidth = 1.5, linetype = 'dashed', color = '#888888')+
  geom_text(data = triggers_clean, aes(x = date-2, y = -9500, label = plot_label), size = 5, fontface = 'bold')+
  labs(y = 'Daily OMRI (cfs)') +
  scale_x_date(date_breaks = '2 weeks', date_labels = '%b %d') +
  scale_color_manual(values = c("#0173B2", "#DE8F05", "#CC78BC"))+
  scale_y_reverse() +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.text = element_text(size = 15),
        axis.title = element_text(size = 15))
omr_plot
```

```{r}
#| label: fig-triggers
#| warning: false
#| fig-cap: "Operations and Action Summary, WY 2026. The numbers and dashed lines in the OMRI plot indicate different triggers (see Table 1), with shading representing specific action periods. OMRI data (colored lines) calculated by SacPAS, Freeport (FPT) and Vernalis (VNS) flow data from CDEC, and CVP (TRP) and SWP (HRO) exports data from CDEC."
#| fig-alt: "Three part plot showing hydrologic conditions over time. Top plot shows a time series of flow at Vernalis and Freeport. The middle plot shows a time series of daily, weekly, and 14-day average OMRI, with vertical lines and shading to show when actions were taken. The lower plot is a column chart showing combined exports from both CVP and SWP."
#| fig-width: 9
#| fig-height: 7
#| echo: false
 
flow_plot +omr_plot + export_plot + plot_layout(nrow = 3)
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-triggers
#| tbl-cap: "Summary of Actions and Triggers, WY 2026"

trigger_table <- triggers_clean %>%
  select(Label = plot_label,
         Action = action,
         `Date Triggered` = date_triggered,
         `Date Implemented` = date_implemented,
         `Number Days Implemented` = days_implemented,
         Regulation = regulation,
         )

flextable(trigger_table) %>%
  font(fontname = "Carlito", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  theme_booktabs() %>%
  fit_to_width(max_width = 6.5)

```

### Zone of Influence

Zone of Influence (ZOI) analysis is discussed in detail in the December 22 assessment. Current conditions were queried from most recent Freeport flow data on the Sacramento River and Vernalis flow data on the San Joaquin river from [SacPAS](https://www.cbr.washington.edu/sacramento/data/query_river_table.html).  Forecasted flows were queried from short range deterministic flows provided by the [California Nevada River Forecast Center](https://www.cnrfc.noaa.gov/deterministicHourlyProductCSV.php).

Current conditions at Freeport and Vernalis indicate that delta hydrology falls within the `r paste0("'",hydrology_current, "'")` category.  Forecasted conditions averaged across the next 7 days falls within the `r paste0("'",hydrology_forecast, "'")` category.

The altered channel length for the current `r paste0('"', hydrology_current, '"')` hydrology is `r length_current` kilometers (km) across OMR bins of `r omr_current` respectively. The altered channel length for forecasted `r paste0('"', hydrology_forecast, '"')` hydrology is `r length_forecast` kilometers (km) across OMR bins of `r omr_forecast` respectively.

Change in altered channel length between OMR levels is `r channel_filter_current$length_change` km for current conditions and `r channel_filter_forecast$length_change` km for forecasted conditions indicating that ZOI impacts across OMR scenarios `r difference` between current and forecasted conditions.  Across the nine hydrology bins, `r channel_length_text`

```{r}
#| label: fig-zoi_graph
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 8
#| include: true
#| out-width: "100%"
#| results: asis
#| fig-cap: "Modeled Zone of Influence at different OMRI scenarios based on current inflow hydrology (left) and forecasted inflow hydrology (right) from the Sacramento River and San Joaquin River"
#| fig-alt: "Two-part figure showing results for current hydrology (left) and forecasted hydrology (right). Each map of the Delta shows contour lines for the extent of the hydrologic footprint for different OMRI scenarios (colors)."

map_file_current <- grep(hydrology_current, mapList, value = TRUE)
map_file_forecast <- grep(hydrology_forecast, mapList, value = TRUE)

current <- image_read(map_file_current) %>% 
  image_ggplot() + 
  ggtitle("Current Flow")

forecast <- image_read(map_file_forecast) %>% 
  image_ggplot() + 
  ggtitle("Forecasted Flow")

(current | forecast)

```

