---
format:
  html:
    toc: true
    standalone: false
    title-block-style: none
  pdf: default
engine: knitr
---

## PRELIMINARY DATA: Assessment for Delta Operations on ESA and CESA-listed Salmonids

Last updated: *`r format(Sys.Date(), "%B %d, %Y")`*

```{r}
#| label: setup
#| echo: false
#| output: false

library(tidyverse)
library(here)
library(kableExtra)
library(flextable)
library(gt)
library(magick)

project <- here()
source(here(project, 'source_code/salmon_code.R'), echo = FALSE)
source(here(project, 'source_code/text_updates.R'), echo = FALSE)
```

### Executive Summary

-   DCC gates are currently closed and is the controlling factor. Gates will continue to operate in accordance to Table 3-6 in the Proposed Action.

-   Winter-run catch is high at delta entry monitoring locations. No loss has yet to occur at export facilities.

-   Central Valley Steelhead catch is low and no loss has yet to occur at export facilities.

### Natural Winter-run Chinook

#### Current Status

*Give update on migration, salvage, monitoring, and STARs patterns.*

`r wr_jpe` Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_wr), '0%', delta_entry_wr)` of length-at-date (LAD) winter-run have entered the delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_wr), '0%', delta_exit_wr)` have exited the delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_wr), '0%', salvage_wr)` of DNA confirmed winter-run have been salvaged.

```{r}
#| label: wr_timing_table
#| echo: false
#| results: asis
#| tbl-cap: Average Percent of annual emigrating population for unclipped LAD winter-run captured at the following locations and LAD and DNA confirmed winter-run salvaged at SWP and CVP Delta facilities for the past 10 years.

if (knitr::is_html_output()) {
  knitr::kable(wr_natural_timing, align = "lrrrrrr")
} else {
  flextable(wr_natural_timing) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = 0.75, unit = "in") %>%
  font(fontname = 'Open Sans Regular', part = "body") %>%
  font(fontname = 'Open Sans Regular', part = "header") %>%
  bold(bold = TRUE, part = "header") %>%
  fontsize(size = 11, part = "header") %>%
  fontsize(size = 10, part = "body")
}

```

#### Annual Loss

`r wr_threshold` `r wr_annual_text`

```{r}
#| label: wr_loss
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Cumulative loss of natural-origin winter-run for WY 2026.  Cumulative loss is based on genetically confirmed winter-run captured in salvage or length-at-date winter-run in which genetic confirmation was unable to be obtained
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2026/LossUnclip_1_DNAWinter_WY.png')

```

#### Weekly Distributed Loss
#### STARs

The Delta STARS Model is an individual-based simulation model that predicts survival, travel time, and routing of juvenile salmon migrating through the Sacramento–San Joaquin River Delta. This model gives insight into survival and routing patterns of winter-run based on most current conditions.

`r stars_text`

```{r}
#| label: stars_survival
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated overall winter-run survival from Knights Landing to Chipps Island.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-1.png')

```

```{r}
#| label: stars_id_survival
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated survival from Knights Landing to Chipps Island of simulate winter-run cohorts that route through the interior delta.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-2.png')

```

```{r}
#| label: stars_id_routing
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated probability of winter-run routing into the interior delta.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-3.png')

```

### Hatchery Winter-run Chinook
#### Current Status
`r wr_hatch_jpe` `r wr_hatchery_releases`

#### Annual Loss

`r wr_hatch_threshold` `r wr_hatchery_loss`

### Central Valley Steelhead

#### Current Status

Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_sh), '0%', delta_entry_sh)` of CCV steelhead have entered the delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_sh), '0%', delta_exit_sh)` have exited the delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_sh), '0%', salvage_sh)` have been salvaged.

```{r}
#| label: sh_timing_table
#| results: asis
#| tbl-cap: 'Average Percent, with 95%CI, of annual emigrating population for unclipped CCV steelhead captured at the following locations and salvaged at SWP and CVP Delta facilities for the past 10 years.'
#| echo: false

if (knitr::is_html_output()) {
  knitr::kable(sh_natural_timing, align = "lrrrrrr")
} else {
  flextable(sh_natural_timing) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = 0.75, unit = "in") %>%
  font(fontname = 'Open Sans Regular', part = "body") %>%
  font(fontname = 'Open Sans Regular', part = "header") %>%
  bold(bold = TRUE, part = "header") %>%
  fontsize(size = 11, part = "header") %>%
  fontsize(size = 10, part = "body")
}

```

#### Annual Loss

`r sh_annual_text`


```{r}
#| label: sh_loss
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Cumulative loss of natural-origin and hatchery steelhead for WY 2026.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2026/LossUnclip_2_Stlhd_WY.png')
```

### Spring-run
#### Current Status
#### Surrogate Releases and Current Loss
### References
