---
format:
  html:
    toc: true
    standalone: false
    title-block-style: none
  pdf:
    fig-dpi: 750
    fig-pos: "H"
  docx:
    fig-dpi: 750
engine: knitr
---

## PRELIMINARY DATA: Assessment for Delta Operations on ESA and CESA-listed Salmonids

Last updated: *`r format(Sys.Date(), "%B %d, %Y")`*

For more detailed data on salmonid conditions in the Delta see corresponding webpage on [SacPAS](https://www.cbr.washington.edu/sacramento/workgroups/salmon_monitoring.html).

```{r}
#| label: setup
#| echo: false
#| output: false

library(tidyverse)
library(here)
library(kableExtra)
library(flextable)
library(magick)

project <- here()
source(here(project, 'source_code/salmon_code.R'), echo = FALSE)
source(here(project, 'source_code/text_updates.R'), echo = FALSE)
```

```{r}
#| label: exec_summary_logic
#| echo: false
#| results: false

library(lubridate)
library(readr)
library(dplyr)

# Helper function to safely get numeric values without crashing
safe_parse <- function(var_name) {
  if (exists(var_name, where = .GlobalEnv) && !is.na(get(var_name))) {
    val <- get(var_name)
    if(is.numeric(val)) return(val)
    return(parse_number(as.character(val)))
  }
  return(0)
}

# --- 1. Action 5 / Entrainment Management Status ---
current_date <- Sys.Date()
is_season_date_range <- month(current_date) %in% c(1, 2, 3, 4, 5, 6)
pct_wr_in_delta <- safe_parse("delta_entry_wr")
pct_sh_in_delta <- safe_parse("delta_entry_sh")

# Triggered if in date range OR if >5% of target species have entered
entrainment_status <- if(is_season_date_range | (pct_wr_in_delta > 5 | pct_sh_in_delta > 5)) {
  "Entrainment management season is **active**."
} else {
  "Entrainment management season is **not active** at this time."
}

# --- 2. Loss Status (From Loss Summary Table) ---
get_loss_val <- function(pattern) {
  if(!exists("loss_summary_table")) return(0)
  loss_summary_table %>%
    filter(grepl("Cumulative Loss Total", data_item, ignore.case = TRUE)) %>%
    select(matches(pattern)) %>%
    pull() %>%
    as.character() %>%
    parse_number() %>%
    sum(na.rm = TRUE)
}

loss_dna_wr    <- get_loss_val("dna_winter_run_chinook")
loss_lad_wr    <- get_loss_val("lad_winter_run_chinook")
loss_hatch_wr  <- get_loss_val("lsnfh_hatchery_cwt_winter_run_chinook")
loss_nat_sh    <- get_loss_val("natural_steelhead")
loss_hatch_sh  <- get_loss_val("hatchery_steelhead")

total_loss <- sum(loss_dna_wr, loss_lad_wr, loss_hatch_wr, loss_nat_sh, loss_hatch_sh, na.rm = TRUE)

salvage_status <- if(total_loss > 0) {
  paste0("Season Loss: **", loss_dna_wr, "** DNA Winter-run, **", 
         loss_lad_wr, "** LAD Winter-run, **", 
         loss_hatch_wr, "** Hatchery Winter-run, **", 
         loss_nat_sh, "** Natural Steelhead, and **", 
         loss_hatch_sh, "** Hatchery Steelhead.")
} else {
  "No salmonid loss has been recorded this season."
}

# --- 3. Presence Logic Helper Function (UPDATED) ---
get_presence_status <- function(species_name, entry_pct, exit_pct, catch_keyword) {
  real_catch <- 0
  if(exists("all_sampling")) {
    real_catch <- all_sampling %>% 
      filter(Location %in% c('Sac Trawl (Sherwood)', 'Sac Seine')) %>% 
      select(contains(catch_keyword)) %>% 
      as.matrix() %>% sum(na.rm = TRUE)
  }
  
  case_when(
    # 1. Emigration Complete (>95% Exited)
    exit_pct >= 95 ~ paste0(species_name, " presence in the Delta is **low** (emigration nearly complete)."),
    
    # 2. Peak Presence (25% - 75% Entry)
    entry_pct >= 25 & entry_pct <= 75 ~ paste0(species_name, " presence in the Delta is **high** (historical peak)."),
    
    # 3. Decreasing Presence (>75% Entry, but still in system)
    entry_pct > 75 & exit_pct < 95 ~ paste0(species_name, " presence in the Delta is **decreasing** (winding down)."),
    
    # 4. Increasing Presence (5% - 25% Entry)
    entry_pct >= 5 & entry_pct < 25 ~ paste0(species_name, " presence in the Delta is **increasing**."),
    
    # 5. Early Detection (Low Hist < 5%, but Real Fish Caught)
    entry_pct < 5 & real_catch > 0 ~ paste0(species_name, " presence in the Delta is **low**, but fish have been **detected** (", real_catch, " captured in Delta monitoring)."),
    
    # 6. Low/Inactive
    TRUE ~ paste0(species_name, " presence in the Delta is **low** (immigration has not peaked).")
  )
}

# Generate Status for Each Run
wr_presence_status <- get_presence_status("Winter-run", safe_parse("delta_entry_wr"), safe_parse("delta_exit_wr"), "Winter")
sh_presence_status <- get_presence_status("Steelhead", safe_parse("delta_entry_sh"), safe_parse("delta_exit_sh"), "Steelhead")
```

### Executive Summary

-   `r entrainment_status`

-   `r salvage_status`

-   `r wr_presence_status`

-   `r sh_presence_status`

### Natural Winter-run Chinook

#### Juvenile Production Estimate

`r wr_jpe`

#### Current Status

*Entry Timing* - Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_wr), '0%', delta_entry_wr)` of length-at-date (LAD) winter-run have entered the delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_wr), '0%', delta_exit_wr)` have exited the delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_wr), '0%', salvage_wr)` of DNA confirmed winter-run have been salvaged.

```{r}
#| label: tbl-wr_timing_table
#| echo: false
#| results: asis
#| warning: false
#| tbl-cap: Average Percent of annual emigrating population for unclipped LAD winter-run captured at the following locations and LAD and DNA confirmed winter-run salvaged at SWP and CVP Delta facilities for the past 10 years.


knitr::kable(wr_natural_timing, align = "lrrrrrr")

```

*Red Bluff Diversion Dam Passage Estimate* - As of `r format(wr_rbdd_date, '%b %d')` estimated passage to date of LAD winter run at Red Bluff Diversion is approximately `r wr_passage` million fish. * *Note that outmigration timing overlaps with spring run migrating fish, and true winter-run abundance likely differs from these estimates.*

*Delta Monitoring* - `r wr_entry_catch` `r wr_delta_catch` `r wr_exit_catch`

#### Annual Loss

`r wr_threshold` As of `r format(Sys.Date()-1, '%B %d')`, cumulative loss of genetically confirmed winter-run is `r wr_loss` or `r wr_perc` of the annual loss threshold. Cumulative loss in the past 7 days has been `r wr_7d`.

```{r}
#| label: fig-wr_loss
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Cumulative loss of natural-origin winter-run for WY 2026.  Cumulative loss is based on genetically confirmed winter-run captured in salvage or length-at-date winter-run in which genetic confirmation was unable to be obtained
#| fig-alt: Line chart of cumulative loss of natural-origin winter-run Chinook Salmon at Delta facilities where daily loss is tracked against the annual threshold.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read(paste0('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY',wy,'/LossUnclip_1_DNAWinter_WY.png'))

```

#### STARS

The Delta STARS Model is an individual-based simulation model that predicts survival, travel time, and routing of juvenile salmon migrating through the Sacramento–San Joaquin River Delta. This model gives insight into survival and routing patterns of winter-run based on most current conditions.

`r stars_text`

```{r}
#| label: fig-stars_survival
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated overall winter-run survival from Knights Landing to Chipps Island.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-alt: Line chart of estimated overall winter-run survival probability from Knights Landing to Chipps Island where the current water year is compared to historical years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-1.png')

```

```{r}
#| label: fig-stars_id_survival
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated survival from Knights Landing to Chipps Island of simulate winter-run cohorts that route through the interior delta.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-alt: Line chart of winter-run survival probability through the interior Delta where the current water year is compared to historical years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-2.png')

```

```{r}
#| label: fig-stars_id_routing
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated probability of winter-run routing into the interior delta.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-alt: Line chart of winter-run routing probability into the interior Delta where the current water year is compared to historical years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-3.png')

```

### Hatchery Winter-run Chinook

#### Hatchery Releases

`r wr_hatchery_releases`

#### Juvenile Production Estimate

`r wr_hatch_jpe`

#### Annual Loss

`r wr_hatchery_loss`

### Natural-origin Central Valley Steelhead

#### Current Status

*Delta Entry Timing* - Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_sh), '0%', delta_entry_sh)` of CCV steelhead have entered the delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_sh), '0%', delta_exit_sh)` have exited the delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_sh), '0%', salvage_sh)` have been salvaged.

```{r}
#| label: tbl-sh_timing_table
#| results: asis
#| tbl-cap: 'Average Percent of annual emigrating population for unclipped CCV steelhead captured at the following locations and salvaged at SWP and CVP Delta facilities for the past 10 years.'
#| echo: false
#| warning: false

knitr::kable(sh_natural_timing, align = "lrrrrrr")

```

*Delta Monitoring* - `r sh_entry_catch` `r sh_delta_catch` `r sh_exit_catch`

#### Annual Loss

As of `r format(Sys.Date()-1, '%B %d')`, cumulative loss of unclipped steelhead is `r sh_loss` or `r sh_perc` of the incidental take limit in the NMFS Biological Opinion. Cumulative loss in the past 7 days has been `r sh_7d`.

```{r}
#| label: fig-sh_loss
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Cumulative loss of natural-origin steelhead for WY 2026.
#| fig-alt: Line chart of cumulative loss of natural-origin Steelhead at Delta facilities where daily loss is tracked against the annual threshold.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read(paste0('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY',wy,'/LossUnclip_2_Stlhd_WY.png'))
```

### Hatchery-origin Central Valley Steelhead

#### Surrogate Releases

There have been a total of `r n_releases` releases totaling `r sh_stocked` steelhead  in Water Year 2026.  JPE for the hatchery releases as of today is `r sh_jpe` based on estimated survivals using forecasted water year types (see details in table below). The annual loss threshold, equal to 1% of the JPE, is currently `r sh_clipped_threshold`, but is subject to change with additional steelhead releases.  

```{r}
#| label: tbl-sh_clipped_table
#| results: asis
#| tbl-cap: 'Summary of steelhead hatchery releases in Water Year 2026'
#| echo: false
#| warning: false

knitr::kable(release_table_print, align = "lrrrrr")

```

Total loss of hatchery-origin steelhead is `r sh_clipped_loss_total` or `r sh_clipped_perc_threshold` of the threshold.  *Note that hatchery origin of salvaged fish can not be determined at this time and salvage is based on the assumption of similar routing and survival probabilities of individual hatchery releases.

```{r}
#| label: fig-sh_hatch_loss
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Cumulative loss of hatchery steelhead for WY 2026.
#| fig-alt: Line chart of cumulative loss of hatchery-origin Steelhead at Delta facilities where daily loss is tracked against the annual threshold.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read(paste0('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY',wy,'/LossClipped_2_StlhdHatch_WY.png'))
```


### Spring-run

#### Current Status

*Delta Entry Timing*- Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_sr), '0%', delta_entry_sr)` of LAD spring run have entered the delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_sr), '0%', delta_exit_sr)` have exited the delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_sr), '0%', salvage_sr)` have been salvaged.

```{r}
#| label: tbl-sr_timing_table
#| results: asis
#| tbl-cap: 'Average Percent of annual emigrating population for LAD Spring-run Chinook Salmon captured at the following locations and salvaged at SWP and CVP Delta facilities for the past 10 years.'
#| echo: false
#| warning: false


knitr::kable(sr_natural_timing, align = "lrrrrrr")

```

*Red Bluff Diversion Dam Passage Estimate* - As of `r format(sr_rbdd_date, '%b %d')` estimated passage to date of LAD spring run at Red Bluff Diversion is approximately `r sr_passage` million fish. * *Note that outmigration timing overlaps with winter run and fall run outmigration, and true spring run abundance likely differs from these estimates.*

*Delta Monitoring*- `r sr_entry_catch` `r sr_delta_catch` `r sr_exit_catch`

#### Surrogate Releases
A total of `r yearling` yearling surrogate fish have been released across `r nrow(subset(sr_surrogate_table, Type == 'Yearling'))` releases and a total of `r yoy` young-of-year surrogate fish have been released across `r nrow(subset(sr_surrogate_table, Type == 'Young-of-year'))` releases.  See details in table below.

```{r}
#| label: tbl-sr_surrogate_table
#| results: asis
#| tbl-cap: 'Spring-run Chinook Salmon Hatchery Surrogate Summary Table.'
#| echo: false
#| warning: false

knitr::kable(sr_surrogate_table_clean, align = "lrrrrrrr")

```

### Evaluation

1.  **What is the probability of exceeding natural or hatchery winter-run Chinook Salmon loss thresholds in the upcoming week?**

2.  **What is the probability of spring-run hatchery Chinook Salmon loss thresholds in the upcoming week?**

3.  **What is the probability of spring-run hatchery Chinook Salmon loss thresholds in the upcoming week?**


### References
