---
format:
  html:
    toc: true
    standalone: false
    title-block-style: none
  pdf: default
  docx:
    tbl-cap-location: top
engine: knitr
---

## PRELIMINARY DATA: Assessment for Delta Operations on ESA and CESA-listed Salmonids

Last updated: *`r format(Sys.Date(), "%B %d, %Y")`*

```{r}
#| label: setup
#| echo: false
#| output: false

library(tidyverse)
library(here)
library(kableExtra)
library(flextable)
library(gt)
library(magick)

project <- here()
source(here(project, 'source_code/salmon_code.R'), echo = FALSE)
source(here(project, 'source_code/text_updates.R'), echo = FALSE)
```

### Executive Summary

-   Entrainment management season is not active at this time.

-   No salmonids have been salvaged this season.

-   Winter-run presence in the delta is high.

### Natural Winter-run Chinook

#### Juvenile Production Estimate

`r wr_jpe`

#### Current Status

*Entry Timing* - Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_wr), '0%', delta_entry_wr)` of length-at-date (LAD) winter-run have entered the delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_wr), '0%', delta_exit_wr)` have exited the delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_wr), '0%', salvage_wr)` of DNA confirmed winter-run have been salvaged.

```{r}
#| label: tbl-wr_timing_table
#| echo: false
#| results: asis
#| tbl-cap: Average Percent of annual emigrating population for unclipped LAD winter-run captured at the following locations and LAD and DNA confirmed winter-run salvaged at SWP and CVP Delta facilities for the past 10 years.

if (knitr::pandoc_to() == "docx") {
  flextable(wr_natural_timing) %>%
    vline() %>%
    hline() %>%
    border_outer() %>%
    width(width = 0.8, unit = "in") %>%
    font(fontname = 'Segoe UI', part = "body") %>%
    font(fontname = 'Segoe UI Semibold', part = "header") %>%
    fontsize(size = 12, part = "header") %>%
    fontsize(size = 11, part = "body")
} else {
  knitr::kable(wr_natural_timing, align = "lrrrrrr")
}

```

*Red Bluff Diversion Dam Passage Estimate* - As of `r format(wr_rbdd_date, '%b %d')` estimated passage to date of LAD winter run at Red Bluff Diversion is approximately `r wr_passage` million fish. * *Note that outmigration timing overlaps with spring run migrating fish, and true winter-run abundance likely differs from these estimates.*

*Delta Monitoring* - `r wr_delta_catch`

#### Annual Loss

`r wr_threshold` `r wr_annual_text`

```{r}
#| label: fig-wr_loss
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Cumulative loss of natural-origin winter-run for WY 2026.  Cumulative loss is based on genetically confirmed winter-run captured in salvage or length-at-date winter-run in which genetic confirmation was unable to be obtained
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2026/LossUnclip_1_DNAWinter_WY.png')

```

#### STARs

The Delta STARS Model is an individual-based simulation model that predicts survival, travel time, and routing of juvenile salmon migrating through the Sacramento–San Joaquin River Delta. This model gives insight into survival and routing patterns of winter-run based on most current conditions.

`r stars_text`

```{r}
#| label: fig-stars_survival
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated overall winter-run survival from Knights Landing to Chipps Island.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-1.png')

```

```{r}
#| label: fig-stars_id_survival
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated survival from Knights Landing to Chipps Island of simulate winter-run cohorts that route through the interior delta.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-2.png')

```

```{r}
#| label: fig-stars_id_routing
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Estimated probability of winter-run routing into the interior delta.  Black line indicates the current water-year, and other colored lines correspond to past water years.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-3.png')

```

### Hatchery Winter-run Chinook

#### Hatchery Releases

`r wr_hatchery_releases`

#### Juvenile Production Estimate

`r wr_hatch_jpe`

#### Annual Loss

`r wr_hatch_threshold` `r wr_hatchery_loss`

### Natural-origin Central Valley Steelhead

#### Current Status

*Delta Entry Timing* - Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_sh), '0%', delta_entry_sh)` of CCV steelhead have entered the delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_sh), '0%', delta_exit_sh)` have exited the delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_sh), '0%', salvage_sh)` have been salvaged.

```{r}
#| label: tbl-sh_timing_table
#| results: asis
#| tbl-cap: 'Average Percent of annual emigrating population for unclipped CCV steelhead captured at the following locations and salvaged at SWP and CVP Delta facilities for the past 10 years.'
#| echo: false

if (knitr::pandoc_to() == "docx") {
  flextable(sh_natural_timing) %>%
    vline() %>%
    hline() %>%
    border_outer() %>%
    width(width = 0.8, unit = "in") %>%
    font(fontname = 'Segoe UI', part = "body") %>%
    font(fontname = 'Segoe UI Semibold', part = "header") %>%
    fontsize(size = 12, part = "header") %>%
    fontsize(size = 11, part = "body")
} else {
  knitr::kable(sh_natural_timing, align = "lrrrrrr")
}
```

*Delta Monitoring* - `r sh_delta_catch`

#### Annual Loss

`r sh_annual_text`

```{r}
#| label: fig-sh_loss
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Cumulative loss of natural-origin and hatchery steelhead for WY 2026.
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY2026/LossUnclip_2_Stlhd_WY.png')
```

### Hatchery-origin Central Valley Steelhead

#### Hatchery Releases

#### Juvenile Production Estimate

### Spring-run

#### Current Status

*Delta Entry Timing*- Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_sr), '0%', delta_entry_sr)` of LAD spring run have entered the delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_sr), '0%', delta_exit_sr)` have exited the delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_sr), '0%', salvage_sr)` have been salvaged.

```{r}
#| label: tbl-sr_timing_table
#| results: asis
#| tbl-cap: 'Average Percent of annual emigrating population for LAD Spring-run Chinook Salmon captured at the following locations and salvaged at SWP and CVP Delta facilities for the past 10 years.'
#| echo: false


if (knitr::pandoc_to() == "docx") {
  flextable(sr_natural_timing) %>%
    vline() %>%
    hline() %>%
    border_outer() %>%
    width(width = 0.8, unit = "in") %>%
    font(fontname = 'Segoe UI', part = "body") %>%
    font(fontname = 'Segoe UI Semibold', part = "header") %>%
    fontsize(size = 12, part = "header") %>%
    fontsize(size = 11, part = "body")
} else {
  knitr::kable(sr_natural_timing, align = "lrrrrrr")
}
```

*Red Bluff Diversion Dam Passage Estimate* - As of `r format(sr_rbdd_date, '%b %d')` estimated passage to date of LAD spring run at Red Bluff Diversion is approximately `r sr_passage` million fish. * *Note that outmigration timing overlaps with winter run and fall run outmigration, and true spring run abundance likely differs from these estimates.*

*Delta Monitoring*- `r sr_delta_catch`

#### Surrogate Releases
A total of `r yearling` yearling surrogate fish have been released across `r nrow(subset(sr_surrogate_table, Type == 'Yearling'))` releases and a total of `r yoy` young-of-year surrogate fish have been released across `r nrow(subset(sr_surrogate_table, Type == 'Young-of-year'))` releases.  See details in table below.

```{r}
#| label: tbl-sr_surrogate_table
#| results: asis
#| tbl-cap: 'Spring-run Chinook Salmon Hatchery Surrogate Summary Table.'
#| echo: false


if (knitr::pandoc_to() == "docx") {
  flextable(sr_surrogate_table_clean) %>%
    vline() %>%
    hline() %>%
    border_outer() %>%
    width(width = 0.75, unit = "in") %>%
    font(fontname = 'Segoe UI', part = "body") %>%
    font(fontname = 'Segoe UI Semibold', part = "header") %>%
    fontsize(size = 12, part = "header") %>%
    fontsize(size = 11, part = "body")
} else {
  knitr::kable(sr_surrogate_table_clean, align = "lrrrrrrr")
}
```

### Evaluation

1.  **After January 1, has the first winter-run Chinook salvage occurred?** These criteria for the start of entrainment management for winter-run Chinook Salmon have not occurred.

### References
