---
format:
  html:
    toc: true
    standalone: false
    title-block-style: none
  pdf:
    fig-dpi: 750
    fig-pos: "H"
  docx:
    fig-dpi: 750
engine: knitr
execute:
  warning: false
---

## Assessment for Delta Operations on Salmonids

Last updated: *`r format(Sys.Date(), "%B %d, %Y")`*

For more detailed data on salmonid conditions in the Delta see corresponding webpage on [SacPAS](https://www.cbr.washington.edu/sacramento/workgroups/salmon_monitoring.html).

```{r}
#| label: setup
#| echo: false
#| output: false

library(tidyverse)
library(here)
library(flextable)
library(magick)

project <- here()
source(here(project, 'source_code/salmon_code.R'), echo = FALSE)
source(here(project, 'source_code/text_updates.R'), echo = FALSE)
source(here(project, 'source_code/salmon_code_rounding_fix.R'), echo = FALSE)
```

### Executive Summary

-   `r entrainment_status`

-   `r salvage_status`

-   `r wr_presence_status`

-   `r sh_presence_status`

### Natural Winter-run Chinook

#### Juvenile Production Estimate

`r wr_jpe`

#### Current Status

*Delta Entry Timing* - Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_wr), '0%', delta_entry_wr)` of length-at-date (LAD) winter-run have entered the Delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_wr), '0%', delta_exit_wr)` have exited the Delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_wr), '0%', salvage_wr)` of DNA confirmed winter-run have been salvaged.

```{r}
#| label: tbl-wr_timing_table
#| echo: false
#| tbl-cap: 'Average percent of annual emigrating population for unclipped LAD winter-run captured at monitoring locations and salvaged at Delta facilities for the past 10 years'

flextable(wr_natural_timing) %>%
  font(fontname = "Carlito", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  theme_booktabs() %>%
  fit_to_width(max_width = 6.5)
```

*Red Bluff Diversion Dam Passage Estimate* - As of `r format(wr_rbdd_date, '%b %d')` estimated passage to date of LAD winter-run at Red Bluff Diversion is approximately `r wr_passage` million fish. *Note that outmigration timing overlaps with spring-run migrating fish, and true winter-run abundance likely differs from these estimates.*

*Delta Monitoring* - `r wr_entry_catch` `r wr_delta_catch` `r wr_exit_catch`

#### Annual Loss

`r wr_threshold` As of `r format(Sys.Date()-1, '%B %d')`, cumulative loss of genetically confirmed winter-run is `r wr_loss` or `r wr_perc` of the annual loss threshold. Cumulative loss in the past 7 days has been `r wr_7d`.

```{r}
#| label: fig-wr_loss
#| echo: false
#| message: false
#| fig-cap: "Cumulative loss of natural-origin winter-run for WY 2026. Cumulative loss is based on genetically confirmed winter-run captured in salvage or length-at-date winter-run in which genetic confirmation was unable to be obtained"
#| fig-alt: "Line chart of cumulative loss of natural-origin winter-run Chinook salmon at Delta facilities where daily loss is tracked against the annual threshold"
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read(paste0('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY',wy,'/LossUnclip_1_DNAWinter_WY.png'))
```

#### STARS

The Delta STARS Model is an individual-based simulation model that predicts survival, travel time, and routing of juvenile salmon migrating through the Sacramento–San Joaquin River Delta. This model gives insight into survival and routing patterns of winter-run based on most current conditions.

`r stars_text`

```{r}
#| label: fig-stars_survival
#| echo: false
#| message: false
#| fig-cap: "Estimated overall winter-run survival from Knights Landing to Chipps Island. Black line indicates the current water-year, and other colored lines correspond to past water years"
#| fig-alt: "Line chart of estimated overall winter-run survival probability from Knights Landing to Chipps Island where the current water year is compared to historical years"
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-1.png')
```

```{r}
#| label: fig-stars_id_survival
#| echo: false
#| message: false
#| fig-cap: "Estimated survival from Knights Landing to Chipps Island of simulated winter-run cohorts that route through the interior Delta. Black line indicates the current water-year, and other colored lines correspond to past water years"
#| fig-alt: "Line chart of winter-run survival probability through the interior Delta where the current water year is compared to historical years"
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-2.png')
```

```{r}
#| label: fig-stars_id_routing
#| echo: false
#| message: false
#| fig-cap: "Estimated probability of winter-run routing into the interior Delta. Black line indicates the current water-year, and other colored lines correspond to past water years"
#| fig-alt: "Line chart of winter-run routing probability into the interior Delta where the current water year is compared to historical years"
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read('https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_02-3.png')
```

### Hatchery Winter-run Chinook

#### Hatchery Releases

`r wr_hatchery_releases`

#### Juvenile Production Estimate

`r wr_hatch_jpe`

#### Annual Loss

`r wr_hatchery_loss`

### Natural-origin Central Valley Steelhead

#### Current Status

*Delta Entry Timing* - Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_sh), '0%', delta_entry_sh)` of CCV steelhead have entered the Delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_sh), '0%', delta_exit_sh)` have exited the Delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_sh), '0%', salvage_sh)` have been salvaged.

```{r}
#| label: tbl-sh_timing_table
#| tbl-cap: 'Average percent of annual emigrating population for unclipped CCV steelhead captured at monitoring locations and salvaged at Delta facilities for the past 10 years'
#| echo: false

flextable(sh_natural_timing) %>%
  font(fontname = "Carlito", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  theme_booktabs() %>%
  fit_to_width(max_width = 6.5)
```

*Delta Monitoring* - `r sh_entry_catch` `r sh_delta_catch` `r sh_exit_catch`

#### Annual Loss

As of `r format(Sys.Date()-1, '%B %d')`, cumulative loss of unclipped steelhead is `r sh_loss` or `r sh_perc` of the annual loss threshold. Cumulative loss in the past 7 days has been `r sh_7d`.

```{r}
#| label: fig-sh_loss
#| echo: false
#| message: false
#| fig-cap: "Cumulative loss of natural-origin steelhead for WY 2026"
#| fig-alt: "Line chart of cumulative loss of natural-origin steelhead at Delta facilities where daily loss is tracked against the annual threshold"
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read(paste0('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY',wy,'/LossUnclip_2_Stlhd_WY.png'))
```

### Hatchery-origin Central Valley Steelhead

#### Surrogate Releases

There have been a total of `r n_releases` releases totaling `r sh_stocked` steelhead in Water Year 2026. JPE for the hatchery releases as of today is `r sh_jpe` based on estimated survivals using forecasted water year types (see details in table below). The annual loss threshold, equal to 1% of the JPE, is currently `r sh_clipped_threshold_fmt`, but is subject to change with additional steelhead releases.

```{r}
#| label: tbl-sh_clipped_table
#| tbl-cap: 'Summary of steelhead hatchery releases in Water Year 2026. JPE calculated using hatchery-specific survival estimates to Delta entry from release location'
#| echo: false

flextable(release_table_print) %>%
  font(fontname = "Carlito", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  theme_booktabs() %>%
  fit_to_width(max_width = 6.5)
```

```{r}
#| label: tbl-survival_estimates
#| tbl-cap: 'Hatchery-specific survival estimates used for JPE calculations'
#| echo: false

# Create the survival estimates table
survival_table <- data.frame(
  Hatchery = c("Coleman NFH", "Feather River Hatchery", "Nimbus Hatchery", "Mokelumne River Hatchery"),
  `Survival Estimate` = c("0.205 – 0.433", "0.09 – 0.45", "0.62 – 0.83", "0.25 – 0.33"),
  Source = c("Sandstrom et al. 2020", "Kurth 2013", "Brodsky et al. 2020", "Del Real et al. 2012"),
  check.names = FALSE
)

flextable(survival_table) %>%
  font(fontname = "Carlito", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  theme_booktabs() %>%
  align(align = "left", j = 1, part = "all") %>%
  align(align = "center", j = 2, part = "all") %>%
  align(align = "left", j = 3, part = "all") %>%
  fit_to_width(max_width = 6.5)
```

Total loss of hatchery-origin steelhead is `r sh_clipped_loss_total` or `r sh_clipped_perc_threshold` of the annual loss threshold. *Note that hatchery origin of salvaged fish can not be determined at this time and salvage is based on the assumption of similar routing and survival probabilities of individual hatchery releases.*

```{r}
#| label: fig-sh_hatch_loss
#| echo: false
#| message: false
#| fig-cap: "Cumulative loss of hatchery steelhead for WY 2026"
#| fig-alt: "Line chart of cumulative loss of hatchery-origin steelhead at Delta facilities where daily loss is tracked against the annual threshold"
#| fig-width: 10
#| fig-height: 8
#| out-width: "75%"

image_read(paste0('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY',wy,'/LossClipped_2_StlhdHatch_WY.png'))
```

### Spring-run Chinook

#### Current Status

*Delta Entry Timing* - Historically, as of `r format(Sys.Date()-1, "%b %d")`, `r if_else(is.na(delta_entry_sr), '0%', delta_entry_sr)` of LAD spring-run have entered the Delta based on Knights Landing RST catch, `r if_else(is.na(delta_exit_sr), '0%', delta_exit_sr)` have exited the Delta based on Chipps Island Trawl Catch, and `r if_else(is.na(salvage_sr), '0%', salvage_sr)` have been salvaged.

```{r}
#| label: tbl-sr_timing_table
#| tbl-cap: 'Average percent of annual emigrating population for LAD spring-run Chinook salmon captured at monitoring locations and salvaged at Delta facilities for the past 10 years'
#| echo: false

flextable(sr_natural_timing) %>%
  font(fontname = "Carlito", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  theme_booktabs() %>%
  fit_to_width(max_width = 6.5)
```

*Red Bluff Diversion Dam Passage Estimate* - As of `r format(sr_rbdd_date, '%b %d')` estimated passage to date of LAD spring-run at Red Bluff Diversion is approximately `r sr_passage` million fish. *Note that outmigration timing overlaps with winter-run and fall-run outmigration, and true spring-run abundance likely differs from these estimates.*

*Delta Monitoring* - `r sr_entry_catch` `r sr_delta_catch` `r sr_exit_catch`

#### Spring-run Surrogate Releases

A total of `r total_sr_released_fmt` spring-run surrogate fish have been released in Water Year 2026, with an estimated Juvenile Production Estimate (JPE) of `r total_sr_jpe_fmt` fish entering the Delta. This includes `r coleman_total_fmt` Coleman Late-Fall Run Chinook (JPE: `r coleman_jpe_fmt`) released from Coleman National Fish Hatchery across `r coleman_n_groups` coded-wire tag groups. See details in table below.

```{r}
#| label: tbl-sr_surrogate_table
#| tbl-cap: 'Spring-run Chinook salmon surrogate releases (all Coleman Late-Fall releases, both production and experimental)'
#| echo: false
#| warning: false

flextable(sr_surrogate_table_clean) %>%
  font(fontname = "Carlito", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  theme_booktabs() %>%
  fit_to_width(max_width = 6.5)
```

#### Annual Loss

The annual loss threshold is 1% of the JPE entering the Delta, which equals `r sr_threshold_fmt` fish. As of `r format(Sys.Date()-1, '%B %d')`, cumulative loss is `r sr_loss_total_fmt` fish or `r sr_loss_perc` of the annual loss threshold.

### Loss Prediction and Trajectories

The following figures display the cumulative loss trajectories relative to historical years ("Spaghetti Plots") and the current loss predictor model outputs for winter-run Chinook salmon and steelhead.

```{r}
#| label: fig-loss-eval
#| echo: false
#| message: false
#| layout-ncol: 1
#| fig-pos: "H"
#| fig-cap: 
#|   - "Natural LAD winter-run Chinook salmon loss cumulative to date with historical years and annual loss threshold"
#|   - "Natural Central Valley steelhead loss cumulative to date with historical years and annual loss threshold"
#|   - "Estimates of winter-run Chinook loss generated by Loss and Salvage Predictor tool"
#|   - "Estimates of steelhead loss generated by Loss and Salvage Predictor tool"
#| fig-alt: 
#|   - "Line chart showing cumulative loss of natural LAD winter-run Chinook salmon for the current water year (black line) compared to historical years (gray lines) with annual loss threshold indicated as a horizontal dashed line"
#|   - "Line chart showing cumulative loss of natural Central Valley steelhead for the current water year (black line) compared to historical years (gray lines) with annual loss threshold indicated as a horizontal dashed line"
#|   - "Graph showing observed cumulative loss of winter-run Chinook salmon (points) with predicted future loss trajectories including mean predictions (line) and 80% credible intervals (shaded area)"
#|   - "Graph showing observed cumulative loss of steelhead (points) with predicted future loss trajectories including mean predictions (line) and 80% credible intervals (shaded area)"

# Define the Base URL
base_url <- paste0('https://www.cbr.washington.edu/sacramento/workgroups/include_gen/WY', wy, '/')

# 1. Genetic winter-run Spaghetti Plot
image_read(paste0(base_url, 'LossUnclip_1_Winter_currhist.png'))

# 2. Natural steelhead Spaghetti Plot
image_read(paste0(base_url, 'LossUnclip_2_Stlhd_currhist.png'))

# 3. Winter-run Loss Predictor (resize to match width of plots above)
image_read(paste0(base_url, 'samt_lsp_winter.png')) %>%
  image_scale("2000x")

# 4. Steelhead Loss Predictor (resize to match width of plots above)
image_read(paste0(base_url, 'samt_lsp_stlhd.png')) %>%
  image_scale("2000x")
```

### Evaluation

1. **What is the probability of exceeding natural or hatchery winter-run Chinook salmon loss thresholds in the upcoming week?**
    
    `r risk_q1`

2. **What is the probability of spring-run hatchery Chinook salmon loss thresholds in the upcoming week?**
    
    `r risk_q2`

3. **What is the probability of hatchery steelhead loss thresholds in the upcoming week?**
    
    `r risk_q3`

\newpage
### References

::: {style="padding-left: 30px; text-indent: -30px;"}
\hangpara{2em}{1} Brodsky, Annie, Steven C. Zeug, Jonathan Nelson, John Hannon, Paul J. Anders, and Bradley J. Cavallo. "Does Broodstock Source Affect Post-Release Survival of Steelhead? Implications of Replacing a Non-Native Hatchery Stock for Recovery." *Environmental Biology of Fishes* 103, no. [cite_start]5 (2020): 437–53. https://doi.org/10.1007/s10641-020-00951-2. [cite: 52, 53]

\hangpara{2em}{1} Del Real, S. Casey, Michelle Workman, and Joseph Merz. "Migration Characteristics of Hatchery and Natural-Origin Oncorhynchus Mykiss from the Lower Mokelumne River, California." *Environmental Biology of Fishes* 94, no. [cite_start]2 (2012): 363–75. https://doi.org/10.1007/s10641-011-9967-z. [cite: 54, 55]

\hangpara{2em}{1} Kurth, R. 2013. Downstream migration success of Feather River Fish Hatchery steelhead smolts under different release strategies. [cite_start]Presentation at Steelhead Management Meeting, California Department of Fish and Wildlife. [cite: 56]

\hangpara{2em}{1} Sandstrom, Philip Thomas, Arnold J. Ammann, Cyril Michel, et al. "Low River Survival of Juvenile Steelhead in the Sacramento River Watershed." *Environmental Biology of Fishes* 103, no. [cite_start]5 (2020): 531–41. https://doi.org/10.1007/s10641-020-00954-z. [cite: 57, 58, 59]
:::
