---
format:
  html:
    toc: true
    standalone: false
    title-block-style: none
  pdf: default
  docx: default
engine: knitr
---

```{r}
#| label: setup
#| echo: false
#| warning: false
#| message: false
#| output: false

library(tidyverse)
library(here)
library(kableExtra)
library(readxl)
library(glue)
library(viridis)
source("smelt_data_extraction.R")
source("smelt_functions.R")
source("smelt_vars.R")
```

## PRELIMINARY DATA: Assessment for Delta Operations on ESA and CESA-listed Osmerids

*BDO Science Division*

Last updated: *`r format(Sys.Date(), "%B %d, %Y")`*

### Executive Summary

Section 3.13.3.4.1 of the Proposed Action and Section 8.1.4. of the Incidental Take Permit provide that during Old and Middle River (OMR) Management, the California Department of Water Resources, in coordination with Reclamation, shall provide State Water Project (SWP) and Central Valley Project (CVP) operational outlooks and assessments on a weekly basis to Water Operations Management Team (WOMT).

```{r, results = 'asis', echo= FALSE}
cat(narrative_text)
```

### Operational and Regulatory Conditions

- See current Weekly Fish and Water Operations Outlook document.
- Additional information also available on the [SacPAS SMT page](https://www.cbr.washington.edu/sacramento/workgroups/delta_smelt.html).

### Evaluation

#### Delta Smelt

##### Current Status 

- **Delta Smelt Life Stages**: `r lifestages`

- The **abundance estimate** as of the week of `r abundance_date` was: `r paste0(abundance, " (95% CL: ", abundance_lcl, " to ", abundance_ucl, ")")`
- A total of `r format(total_released, scientific = FALSE, big.mark = ",")` hatchery Delta Smelt have been released for WY 2026 (@tbl-ds-releases). The most recent releases of `r format(last_release_count, scientific = FALSE, big.mark = ",")` fish occurred in `r format(last_release_location, scientific = FALSE, big.mark = ",")` on `r format(last_release_date, "%b %d, %Y")`.
- A total of `r adults_count` adult Delta Smelt have been detected this water year. See @fig-ds-map for spatial distribution and @fig-ds-catch for temporal distribution.
- Delta Smelt Salvage totals `r ds_salvage_count` Delta Smelt, and the cumulative seasonal salvage is `r ds_cumsalvage`. 

###### Notes
- Since there are few recent detections of Delta Smelt, the Smelt Monitoring Team’s capacity to estimate where they are within the Delta is limited. 
- See [SacPAS SMT Page](https://www.cbr.washington.edu/sacramento/workgroups/delta_smelt.html) for additional details on detection in surveys and salvage.
- Historical salvage trends can be found at: [SacPAS Salvage Timing](https://www.cbr.washington.edu/sacramento/data/query_salvage_hrt.html)
  
###### Table 1. Delta Smelt Release Summary

```{r, echo = FALSE}
#| label: "tbl-ds-releases"
#| tbl-cap: "Delta Smelt Water Year 2026 Releases"

kable(releases)
```

- *Release event 4 is tentative for planning purposes if extra fish are available and need to be released
- **Total does not account for the tentative release event 4.

###### Figure 1. Distribution

We might have a switch between when it's adult vs juvenile season
```{r, echo = FALSE}
#| fig-width: 8
#| fig-height: 7
#| label: "fig-ds-map"
#| fig-cap: "Delta Smelt Distribution"
(map_detections_lj <- ggplot() + 
    geom_sf(data = WW_Delta, color = "darkslategray3") +
    geom_sf(data = R_EDSM_Strata_1718P1, aes(fill = Stratum), alpha = 0.4,inherit.aes = FALSE)+
    # geom_sf(data = releases_sf, shape = 23, size =3,  fill = "red", color = "black", inherit.aes = FALSE) + 
    geom_sf(data = ds_latlon, aes(shape = source, size = total_catch),   inherit.aes = FALSE) + 
    # geom_sf_text(data = sls_sf, mapping = aes(label = Station), size = 3, nudge_x = -0.012, nudge_y = 0.016) +
    annotation_north_arrow(location = "tl", which_north = "true",
                           pad_x = unit(.1, "in"), pad_y = unit(0.2, "in"),
                           style = north_arrow_fancy_orienteering) +
    annotation_scale(location = "bl", bar_cols = c("black", "white", "black", "white")) +
    scale_x_continuous(limits = c(-122.35, -121.3)) + 
    scale_y_continuous(limits = c(37.8, 38.6)) +
    scale_shape_manual(values = c(15, 17, 4))+
    scale_size(range = c(2, 2), breaks = c(1,1)) + 
    viridis::scale_fill_viridis(option = "turbo", discrete = TRUE) + 
    guides(fill = guide_legend(nrow = 3, byrow = TRUE)) +
    theme_bw() +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text = element_text(size = 10),
          axis.text.x = element_text(angle = 45, vjust = 0.5),
          legend.position = "top",
          legend.box = "vertical",
          legend.title = element_blank(),
          legend.text = element_text(size = 9)))
```

**Do we still want catch tables or just to modify tables on SacPAS - recent (2 wk) and water year totals**

###### Table 2. Total Catch by survey
```{r, echo = FALSE, message = FALSE}
#| label: "tbl-catch-all"
#| tbl-cap: "Delta Smelt Water Year Totals by Life Stage"
kable(
  ds_detail %>%
  group_by(source, region, life_stage) %>%
    summarize(total = sum(catch)) %>%
    ungroup()
)
```


###### Figure 2. Plot of catch over time
```{r, echo = FALSE}
#| label: "fig-ds-catch"
#| fig-cap: "Delta Smelt Catch Over Time"
ggplot(ds_latlon) +
  geom_col(aes(date, total_catch, fill = source)) +
  scale_fill_viridis(option = "turbo", discrete = TRUE) +
  theme_bw()
```

##### Environmental Surrogates

###### Relevant Weather Forecasts
```{r, echo=FALSE, results='asis'}
cat(glue("
- {weather_stockton}
- {weather_antioch}
"))
```
- Weather forecasts for [Stockton, CA](https://forecast.weather.gov/MapClick.php?lat=37.9537&lon=-121.2905#.Y2qMENeIaUk) and [Antioch, CA](https://forecast.weather.gov/MapClick.php?lat=38.0169&lon=-121.8138) as of `r format(Sys.Date(), "%B %d, %Y")`.



###### Actions

- We could pull the SacPAS plots if we want for each relevant metric (or create our own)

####### First Flush
```{r, echo = FALSE, results='asis'}
if (first_flush_status != "relevant") {
  cat("- Not relevant\n")
} else {
  cat(glue("
- **Threshold**: 3-day avg FPT flow ≥ 25,000 cfs and 3-day avg FPT turbidity ≥ 50 FNU  
- **FPT Flow (3-day average)**: {format(FPT_flow_avg, big.mark = ",")} cfs as of {format(env_last_date, '%b %d, %Y')}
- **FPT Turbidity (3-day average)**: {FPT_turb_avg} FNU as of {format(env_last_date, '%b %d, %Y')}
"))
}
```

####### Entrainment Actions

######## Adult Delta Smelt

```{r, echo = FALSE, results='asis'}
if (adult_ent_status != "relevant") {
  cat("- Not relevant\n")
} else {
  cat(glue("
- **Threshold**: Turbidity ≥ 12 FNU at OBI, HOL and OSJ
- **OBI Turbidity**: {paste(OBI_turb, collapse = ', ')} FNU as of {format(env_last_date, '%b %d, %Y')}
- **HOL Turbidity**: {paste(HOL_turb, collapse = ', ')} FNU as of {format(env_last_date, '%b %d, %Y')}
- **OSJ Turbidity**: {paste(OSJ_turb, collapse = ', ')} FNU as of {format(env_last_date, '%b %d, %Y')}
"))

  cat(glue("
- <u>**Offramp Adult/Onramp Larval and Juvenile Protections** when RVB or SJJ > 12°C</u>
- **RVB temperature (3-day average)**: {RVB_temp}°C as of {format(env_last_date, '%b %d, %Y')}
- **SJJ temperature (in the future)**:
"))
}
```

- See [Bay-Delta Live](https://www.baydeltalive.com/current_conditions/constituent-tracker-turbidity) for recent Delta-wide turbidity conditions.
- Let's link to wind plot on the other SacPAS SMT page. 

####### Larval/Juvenile Delta Smelt
Currently Secchi depth; move towards turbidity
```{r, echo = FALSE, results='asis'}
if (larval_ent_status != "relevant") {
  cat("- Not relevant\n")
} else {
  cat(glue("
  - **Threshold**: Secchi Depth > 1m
  - **12-station South Delta Secchi Depth**: The most recent average secchi depth was {sd_secchi_depth}m as of {format(sd_secchi_date, '%b %d, %Y')}
"))
}
```


#### Longfin Smelt

For Action 5, these rely on JPF (unsure how this is calculated) and population models (which don't yet exist)

##### Adult Entrainment
```{r}

```

##### Larval/Juvenile Entrainment 
```{r}

```








###### End of Smelt OMR Management
```{r, echo = FALSE, results='asis'}
if (end_of_season != "relevant") {
  cat("- Not relevant\n")
} else {
  cat(glue("
- **Threshold**: CLC > 25° for 3 consecutive days 
- Clifton Court Temperature: {paste(CLC_temp, collapse = ', ')}°C as of {format(env_last_date, '%b %d, %Y')}
"))
}
```

  
###### Zone of Influence/PTM: 

### References



