---
execute:
  echo: false
  warning: false
  error: false
format:
  html:
    toc: true
    toc-depth: 4
    toc-expand: true
    toc-location: left
    number-sections: false
    theme: cosmo
    smooth-scroll: true
    css: styles.css
editor: visual
---

```{r}
#| label: setup
#| include: false

library(knitr)
library(readr)
library(dplyr)
library(kableExtra)
library(readxl)
library(tidyr)
source("helper_functions.R")

selected_results_folder <- get_selected_results_folder("..", "report_config.yml")
selected_results_name <- basename(selected_results_folder)

# Extract forecast start date from folder name, e.g., 20260526_results
forecast_start_date <- as.Date(
gsub("_results", "", selected_results_name),
format = "%Y%m%d"
)

forecast_end_date <- forecast_start_date + 20

week1_start <- forecast_start_date
week1_end <- forecast_start_date + 6

week2_start <- forecast_start_date + 7
week2_end <- forecast_start_date + 13

week3_start <- forecast_start_date + 14
week3_end <- forecast_start_date + 20

fmt_date <- function(x) {
format(x, "%m/%d/%Y")
}
fmt_long_date <-function(x){
  format(x, "%B %d, %Y")
}
```

# Delta Real-Time Forecast Summary

Date Published: *`r format(Sys.Date(), "%B %d, %Y")`*

Forecast Period: `r fmt_date(forecast_start_date)` – `r fmt_date(forecast_end_date)`

Forecast Week 1: `r fmt_date(week1_start)` – `r fmt_date(week1_end)`

Forecast Week 2: `r fmt_date(week2_start)` – `r fmt_date(week2_end)`

Forecast Week 3: `r fmt_date(week3_start)` – `r fmt_date(week3_end)`

## Common Assumptions

{{< include common_assumptions.md >}}

## Reclamation Forecast Flow and Export Data
```{r, echo = FALSE}
#| label: tbl-zoi
#| tbl-cap: "Weekly Averaged Forecasted Flow Data and Flow Bins"

create_zoi_table(selected_results_folder)
```
::: {.key}
Key: cfs = cubic feet per second, Sac = Sacramento River, SJR = San Joaquin River
:::
```{r}
#| label: tbl-average-exports
#| tbl-cap: "Weekly Averaged CVP and SWP Exports by OMR Bin"

create_average_exports_table(selected_results_folder)
```
::: {.notes}
Notes:

¹ One pumping unit is currently out of service at Jones Pumping Plant until August 2026. The current maximum

² Per the State Water Project (SWP) Incidental Take Permit (ITP) 8.12.1, the State is required to curtail exports April 1 through May 31. This change in exports is expected to persist for the two-month period unless Vernalis flows change. This is reflected in the forecast SWP exports starting on April 1.

³ There is still a low probability an OMR of -6,500 cfs would be realized, so that scenario is omitted from this assessment.
:::

::: {.key}
Key: cfs = cubic feet per second, CVP = Central Valley Project, OMR = Old and Middle River
:::
```{r}
#| label: fig-flow-export
#| fig-cap: "Daily Average Flow for Measured and Forecasted Delta Inflow, CVP Exports, and SWP Exports"
#| out-width: "100%"

insert_flow_export_figure(selected_results_folder)
```
::: {.key}
Key: CVP = Central Valley Project, OMR = Old and Middle River, SWP = State Water Project
:::
## Delta Export Zone of Influence
```{r}
#| label: fig-zoi-week1
#| fig-cap: "**Delta Zone of Influence for Week 1**"
#| out-width: "80%"

insert_zoi_figure(selected_results_folder, 1)
```
::: {.notes}
Notes: Contours indicate the proportional overlap of hourly average velocity Gaussian KDEs for a 1-week period from DSM2 hydro simulations with and without Delta exports active. DSM2 nodes that were sufficiently different from neighboring nodes to create isolated contours at several OMR flows were removed (nodes 146, 147, 148, 206, 242, 246, 432, 433, 434).
:::

::: {.key}
Key: cfs = cubic feet per second, OMR = Old and Middle River
:::
```{r}
#| label: fig-zoi-week2
#| fig-cap: "**Delta Zone of Influence for Week 2**"
#| out-width: "80%"

insert_zoi_figure(selected_results_folder, 2)
```
::: {.notes}
Notes: Contours indicate the proportional overlap of hourly average velocity Gaussian KDEs for a 1-week period from DSM2 hydro simulations with and without Delta exports active. DSM2 nodes that were sufficiently different from neighboring nodes to create isolated contours at several OMR flows were removed (nodes 146, 147, 148, 206, 242, 246, 432, 433, 434).
:::

::: {.key}
Key: cfs = cubic feet per second, OMR = Old and Middle River
:::

```{r}
#| label: fig-zoi-week3
#| fig-cap: "**Delta Zone of Influence for Week 3**"
#| out-width: "80%"

insert_zoi_figure(selected_results_folder, 3)
```
::: {.notes}
Notes: Contours indicate the proportional overlap of hourly average velocity Gaussian KDEs for a 1-week period from DSM2 hydro simulations with and without Delta exports active. DSM2 nodes that were sufficiently different from neighboring nodes to create isolated contours at several OMR flows were removed (nodes 146, 147, 148, 206, 242, 246, 432, 433, 434).
:::

::: {.key}
Key: cfs = cubic feet per second, OMR = Old and Middle River
:::

```{r}
#| label: tbl-channel-length
#| tbl-cap: "Proportion of DSM2 Channel Length with Hydrologic Alteration from Pumping"

create_channel_length_table(selected_results_folder)
```
::: {.notes}
Notes: Sum channel length includes the length of channels within the Delta that have a calculated hydrologic alteration level falling within each category.
:::

::: {.key}
Key: HA = hydrologic alteration, OMR = Old and Middle River
:::

```{r}
#| label: fig-channel-length-week1
#| fig-cap: "Proportional Channel Length for Week 1"
#| out-width: "100%"

insert_proportional_channel_length_figure(selected_results_folder, 1)
```

```{r}
#| label: fig-channel-length-week2
#| fig-cap: "Proportional Channel Length for Week 2"
#| out-width: "100%"

insert_proportional_channel_length_figure(selected_results_folder, 2)
```

```{r}
#| label: fig-channel-length-week3
#| fig-cap: "Proportional Channel Length for Week 3"
#| out-width: "100%"

insert_proportional_channel_length_figure(selected_results_folder, 3)
```
::: {.key}
Key: cfs = cubic feet per second, OMR = Old and Middle River
:::

## PTM (Particle Tracking Model) Results

**PTM Flux Evaluation Period:** `r fmt_date(forecast_start_date)` – `r fmt_date(forecast_end_date)`

**Particles Injected:** `r fmt_date(week1_start)`
```{r}
#| label: fig-ptm-injection-flux-locations
#| fig-cap: "Map of PTM Injection and Flux Locations"
#| out-width: "85%"

insert_static_figure("ptm_injection_flux_locations.png")
```

### Neutrally Buoyant Particles (NP)
```{r}
#| label: tbl-np-chipps
#| tbl-cap: "Neutral Particle Fate (percent flux across boundary) for Particles Injected at Chipps (DSM2 Node 465)"

create_ptm_fate_table(selected_results_folder, "NP_465(Chipps).csv")
```

::: {.notes}
**Note:** Values between 0.0 and 0.1 are indicated with <0.1.
:::

::: {.key}
*Key: CVP = Central Valley Project, OMR = Old and Middle River, SWP = State Water Project*
:::

```{r}
#| label: tbl-np-cache-slough
#| tbl-cap: "Neutral Particle Fate (percent flux across boundary) for Particles Injected at Cache Slough (DSM2 Node 350)"

create_ptm_fate_table(selected_results_folder, "NP_350(Cache Slough).csv")
```

::: {.notes}
**Note:** Values between 0.0 and 0.1 are indicated with <0.1.
:::

::: {.key}
*Key: CVP = Central Valley Project, OMR = Old and Middle River, SWP = State Water Project*
:::

```{r}
#| label: tbl-np-jersey-point
#| tbl-cap: "Neutral Particle Fate (percent flux across boundary) for Particles Injected at Jersey Point (DSM2 Node 469)"

create_ptm_fate_table(selected_results_folder, "NP_469(Jersey Point).csv")
```

::: {.notes}
**Note:** Values between 0.0 and 0.1 are indicated with <0.1.
:::

::: {.key}
*Key: CVP = Central Valley Project, OMR = Old and Middle River, SWP = State Water Project*
:::

```{r}
#| label: tbl-np-old-river
#| tbl-cap: "Neutral Particle Fate (percent flux across boundary) for Particles Injected at Old River (DSM2 Node 99)"

create_ptm_fate_table(selected_results_folder, "NP_99(Old River).csv")
```

::: {.notes}
**Note:** Values between 0.0 and 0.1 are indicated with <0.1.
:::

::: {.key}
*Key: CVP = Central Valley Project, OMR = Old and Middle River, SWP = State Water Project*
:::
```{r}
#| label: fig-np-465-a
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -5,000 cfs. Particles Injected at DSM2 Node 465 (Chipps)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_02_465A.png")
```

```{r}
#| label: fig-np-465-b
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -3,500 cfs. Particles Injected at DSM2 Node 465 (Chipps)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_03_465B.png")
```

```{r}
#| label: fig-np-465-c
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -2,000 cfs. Particles Injected at DSM2 Node 465 (Chipps)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_04_465C.png")
```

```{r}
#| label: fig-np-350-a
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -5,000 cfs. Particles Injected at DSM2 Node 350 (Cache Slough)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_06_350A.png")
```

```{r}
#| label: fig-np-350-b
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -3,500 cfs. Particles Injected at DSM2 Node 350 (Cache Slough)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_07_350B.png")
```

```{r}
#| label: fig-np-350-c
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -2,000 cfs. Particles Injected at DSM2 Node 350 (Cache Slough)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_08_350C.png")
```

```{r}
#| label: fig-np-469-a
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -5,000 cfs. Particles Injected at DSM2 Node 469 (Jersey Point)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_10_469A.png")
```

```{r}
#| label: fig-np-469-b
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -3,500 cfs. Particles Injected at DSM2 Node 469 (Jersey Point)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_11_469B.png")
```

```{r}
#| label: fig-np-469-c
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -2,000 cfs. Particles Injected at DSM2 Node 469 (Jersey Point)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_12_469C.png")
```

```{r}
#| label: fig-np-99-a
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -5,000 cfs. Particles Injected at DSM2 Node 99 (Old River)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_14_99A.png")
```

```{r}
#| label: fig-np-99-b
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -3,500 cfs. Particles Injected at DSM2 Node 99 (Old River)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_15_99B.png")
```

```{r}
#| label: fig-np-99-c
#| fig-cap: "PTM Results for Neutral Particles. OMR Scenario -2,000 cfs. Particles Injected at DSM2 Node 99 (Old River)"
#| out-width: "85%"

insert_ptm_figure(selected_results_folder, "NP_16_99C.png")
```





### Surface Oriented Particles (PP)

## ECO-PTM (Ecological Particle Tracking Model)

## Longfin Smelt Larval Population and PTM Analysis

------------------------------------------------------------------------

## 
