---
execute:
  echo: false
  warning: false
  error: false
format:
  html:
    toc: true
    toc-depth: 4
    toc-expand: true
    toc-location: left
    number-sections: false
    theme: cosmo
    smooth-scroll: true
editor: visual
---

```{r}
#| label: setup
#| include: false

library(knitr)
library(readr)
library(dplyr)
library(kableExtra)
source("helper_functions.R")

selected_results_folder <- get_selected_results_folder("..", "report_config.yml")
selected_results_name <- basename(selected_results_folder)

# Extract forecast start date from folder name, e.g., 20260526_results
forecast_start_date <- as.Date(
gsub("_results", "", selected_results_name),
format = "%Y%m%d"
)

forecast_end_date <- forecast_start_date + 20

week1_start <- forecast_start_date
week1_end <- forecast_start_date + 6

week2_start <- forecast_start_date + 7
week2_end <- forecast_start_date + 13

week3_start <- forecast_start_date + 14
week3_end <- forecast_start_date + 20

fmt_date <- function(x) {
format(x, "%m/%d/%Y")
}
fmt_long_date <-function(x){
  format(x, "%B %d, %Y")
}
```

# Delta Real-Time Forecast Summary

Date Published: *`r format(Sys.Date(), "%B %d, %Y")`*

Forecast Period: `r fmt_date(forecast_start_date)` – `r fmt_date(forecast_end_date)`

Forecast Week 1: `r fmt_date(week1_start)` – `r fmt_date(week1_end)`

Forecast Week 2: `r fmt_date(week2_start)` – `r fmt_date(week2_end)`

Forecast Week 3: `r fmt_date(week3_start)` – `r fmt_date(week3_end)`

## Common Assumptions

{{< include common_assumptions.md >}}

## Reclamation Forecast Flow and Export Data

**Table 1. Weekly Averaged Forecasted Flow Data and Flow Bins**

```{r}
#| echo: false

create_zoi_table(selected_results_folder)
```

*Key: cfs = cubic feet per second, Sac = Sacramento River, SJR = San Joaquin River*

**Table 2. Weekly Averaged CVP and SWP Exports by OMR Bin**

```{r}
#| label: table-average-exports
#| echo: false

create_average_exports_table(selected_results_folder)
```

**Notes:**

¹ One pumping unit is currently out of service at Jones Pumping Plant until August 2026. The current maximum

² Per the State Water Project (SWP) Incidental Take Permit (ITP) 8.12.1, the State is required to curtail exports April 1 through May 31. This change in exports is expected to persist for the two-month period unless Vernalis flows change. This is reflected in the forecast SWP exports starting on April 1.

³ There is still a low probability an OMR of -6,500 cfs would be realized, so that scenario is omitted from this assessment.

*Key: cfs = cubic feet per second, CVP = Central Valley Project, OMR = Old and Middle River*

## Delta Export Zone of Influence

## PTM (Particle Tracking Model) Results

### Neutrally Buoyant Particles (NP)

### Surface Oriented Particles (PP)

## ECO-PTM (Ecological Particle Tracking Model)

## Longfin Smelt Larval Population and PTM Analysis

------------------------------------------------------------------------

## 
